%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{bookmark}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}

\name{Pouya Aghahoseini} % Your name

\address{76 John Angus Drive, Winnipeg, Manitoba, Canada R3Y 0C4. \\ (+98)9102117201 }
\address{\href{mailto:pouyaaghahoseini@gmail.com}{\Large\faEnvelope \hspace{3pt}  } \\ \href{https://github.com/pouyaaghahoseini}{\hspace{3pt} \Large\faGithub \hspace{3pt} } \\ \href{https://linkedin.com/in/pouyaaghahoseini}{\hspace{3pt} \Large\faLinkedin  \hspace{3pt}} \\
	\href{http://pouyaaghahoseini.github.io}{\hspace{5pt} \Large\faGlobe} }
\address {Curriculum vitae last updated on \today}

\begin{document}
	
	%	RESEARCH ‌INTEREST SECTION
	%----------------------------------------------------------------------------------------	
	\begin{rSection}{Research Interests}
			\textbf{ $\bullet$ Human-Computer Interaction}\hspace*{16pt}
			\textbf{ $\bullet$ Machine Learning}\hspace*{16pt}
			\textbf{$\bullet$ Natural Language Processing} \hspace*{16pt}\\
			\textbf{ $\bullet$ Computer Vision}\hspace*{16pt}
			\textbf{ $\bullet$ Reinforcement Learning}\hspace*{16pt}
			\textbf{ $\bullet$ Social Media Computing}	\hspace*{16pt}	
%			\textbf{ $\bullet$ Information Retrieval}\hspace*{16pt}


	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Education}
		{\bf Master of Science in Computer Science} \hfill {\em 2021-2022(Expected)} \\ 
		
		{\bf Bachelor of Science in Computer Science} \hfill {\em 2016-2020} \\ 
		\href{https://www.topuniversities.com/universities/amirkabir-university-technology}{\textcolor{coolblack}{Amirkabir University of Technology(Tehran Polytechnic), Tehran, Iran} }\\
		CGPA: 3.6/4 (17.16/20)\\
		Last Two Years GPA(68 Credits): 3.76/4 (18.45/20) \hspace{20pt}		Selected Courses
		\footnote{\textit{Introduction to Probability, Probability 1:$A^{+}$ }; \textcolor{blue}{Foundation of Matrix and Linear Algebra:$A$ }; \textit{Foundation of Numerical Analysis:$A^{+}$ };  \textcolor{blue}{Data Structures and Algorithms:$A^{+}$ }; \textit{Database:$A$ }; \textcolor{blue}{Software Design:$A$} ; \textit{Design and Analysis of Algorithm:$A^{+}$}} \\
		{\bf Diploma in Mathematics and Physics} \hfill {\em 2012-2016}\\ 
		Allameh Helli High School, Tehran , Iran (NODET)\\
		GPA: 18.5/20
	\end{rSection}
		%----------------------------------------------------------------------------------------
	%	RESEARCH EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Research Experience}
		
			\begin{rSubsection}{\href{https://www.researchgate.net/publication/337632914_Short_Text_Similarity_A_Survey}{\textcolor{coolblack}{Short Text Similarity: A Survey}}}{Nov 2019}{Literature Review}{ }
		\item A Comprehensive Survey on works done in the area of Short Text Similarity from 2004 to 2019
	\end{rSubsection}
	\end{rSection}
	%----------------------------------------------------------------------------------------
	%	TEACHING EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Teaching Experience}
		\begin{rSubsection}{TA, Design and Analysis of Algorithms}{Feb 2020 - Aug 2020}{Instructor: Dr.MohammadReza Kazemi}{ }
		\item Holding Classes
		\item Designing and Evaluating Assignments
		\end{rSubsection}				
		\begin{rSubsection}{Head TA, Fundamentals of Programming: C Language}{Sep 2019 - Jan 2020}{Instructor: Dr.Farzaneh Salari}{ }
		\item Holding Weekly Workshops
		\item Holding Office Hours
		\item Designing and Evaluating Assignments
		
		\end{rSubsection}					%------------------------------------------------
		\begin{rSubsection}{TA, Compilers}{Sep 2019 - Jan 2020}{Instructor: Dr.Mohammad Hassan Shirali-Shahreza}{ }
		\item Exam Preperation Classes and Assignment Evaluation
		\end{rSubsection}					%------------------------------------------------
		\begin{rSubsection}{TA, Data Structures and Algorithms }{Feb 2019 - Jun 2019}{Instructor: Dr.Mohammad Akbari}{ }
			\item 
			Held weekly classes and office hours.
			\item 
			Designed and Evaluated assignment and projects.\\
		\end{rSubsection}
		%------------------------------------------------
		\begin{rSubsection}{Head TA, Introduction to the Theory of Computation}{Sep 2018 - Jan 2019}{Instructor: Dr.Fatemeh Zare-Mirakabad}{ }
			\item Held weekly classes 
			\item Supervised monthly workshops
			\item Designed and Evaluated assignment 		
		\end{rSubsection}
		%-----------------------------------------------
		
	\end{rSection}
		%----------------------------------------------------------------------------------------
	%	EXTRACURRICULAR EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Extracurricular Experience}
		\begin{rSubsection}{Winter School Organizing Committee Member}{Mar 2019}{11th Winter School on Computational Geometry}{ }
			\item 	The Winter School on Computational Geometry is held every year by Math and Computer Science Faculty, in collaboration with IPM Institute for Research in Fundamental Sciences.
			\item Notable researchers in computational geometry are invited for seminars and workshops in this program.
		\end{rSubsection}
		%-------------------------------------------------------------------------
		\begin{rSubsection}{Student Scientific Chapter Membership}{Mar 2018 - Mar  2019}{Head Of Informatics and Competitions}{ }
			\item Organized Data Science Seminars And Workshops.
			\item Coordinated 5 ACM Contests.
			\item Arranged On-Site Visits To Leading Tech Companies In Tehran.
			\item Arranged Talks With Alumni Currently Studying Or Working Abroad.
			\item Held 2018 New Student Orientation Program.
			\item Organized And Instructed Exam Preparation Classes(Calculus, Programming, Differential Equations).
		\end{rSubsection}
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	PROJECTS SECTION
	%---------------------------------------------------------------------------------------
	\begin{rSection}{Projects}

		\begin{rSubsection}{Factory Simulation with MATLAB}{Sep 2018 - Jan 2019}{\href{https://github.com/pouyaaghahoseini/System-Queueing-Simulation}{\textcolor{coolblack}{Simulation  Project}}}{ }
			\item System modeling and simulation with MATLAB
			\item Simulation of a factory with different performances and various response time of each agent.
			
			
		\end{rSubsection}
	
		\begin{rSubsection}{Medify: An Application for Fixing Tags And Organizing Media Files}{Jan 2018 - July 2018}{\href{https://github.com/pouyaaghahoseini/Medify}{\textcolor{coolblack}{Software Engineering Course Project}}}{ }
			
			\item The application was Developed using Scrum Methodology for Agile Software Development.
			\item The coursework required 5 presentations throughout the semester which included a 5-minute startup pitch presentation and the presentation of the first MVP(Minimum Viable Product).
		\end{rSubsection}
		
		\begin{rSubsection}{Designing and Creating A Database From YAGO Datasets}{Jan 2018 - July 2018}{\href{https://github.com/pouyaaghahoseini/Database-Course}{\textcolor{coolblack}{Database Course Project}}}{ }
			\item Data Extraction using TSV files acquired from \href{https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/}{max plank institute website}.
			\item Processing and Clustering TSV files with Python and MySQL.
			\item Designing and Creating A 3NF Database.
			
		\end{rSubsection}	
		
		
		\begin{rSubsection}{\href{https://github.com/pouyaaghahoseini/DS-Course/tree/master/SE-Skiplist}{\textcolor{coolblack}{SESSET: A Space Efficient Skiplist Data Structure}}}{Sep 2017 - January 2018}{Data Structures Course Project}{ }
			\item SSET‌ was implemented with skiplist data structure.
			\item Each node consisted a BDeque which resulted in more efficient operations.
			\item All operations are done in $O(logn)^{E} + O(\sqrt{n})$ time.
		\end{rSubsection}
		
		
		\begin{rSubsection}{\href{https://github.com/pouyaaghahoseini/DS-Course}{\textcolor{coolblack}{Range-Tree: A 2-D version of Range-Tree Data Structure}}}{Sep 2017 - January 2018}{Data Structures Course Project}{ }
			\item An Efficient Data Structure for geometrical queries.
		%	\item The Tree is primarily built with the input points.
		%	\item Queries are asked in the form of rectangle coordinates. 
		%	\\
		\end{rSubsection}
	\end{rSection}
	%----------------------------------------------------------------------------------------
	%	HONORS AND AWARDS SECTION
	%----------------------------------------------------------------------------------------\\
	\begin{rSection}{Honors and Awards}
		\begin{rSubsection}{IGSES}{Jan 2021}{University of Manitoba}{ }
			\item International Graduate Student Entrance Scholarship
		\end{rSubsection}
		
		\begin{rSubsection}{Top 10\% in Graduating Class}{Aug 2020}{Math and Comptuer Science Faculty}{ }
			\item Class of 70 students
		\end{rSubsection}
		
		\begin{rSubsection}{Ranked $1^{st}$ GPA at Fall-2018 and Spring-2019 Semesters }{Sep 2018 - Jun 2019}{Math and Comptuer Science Faculty}{ }
			\item Class of 70 Students
		\end{rSubsection}	
		
		\begin{rSubsection}{Qualified for the final round of Amirkabir ACM-ICPC Competition}{Nov 2018}{Computer Engineering Faculty}{ }
			\item The ACM-ICPC Contest is held every year at Amirkabir University of Technology. Teams from all universities across the country take part in this competition.
			\item Candidates for representing the university in Asia Region contest are primarily filtered here.
		\end{rSubsection}
		
		\begin{rSubsection}{Ranked Within the Top 0.7\% (1,169 among 162,879 students) in Iranian University Entrance Exam}{Jul 2016}{Tehran, Iran }{ }
			\item The competition is intense since it is the only means to gain admission to universities.
		\end{rSubsection} 
		
		\begin{rSubsection}{Accepted in NODET (National Organization for Development of Exceptional Talents) High School Entrance Exam}{Jul 2012}{Tehran, Iran }{ }
			\item NODET student selection exam is held every year nationwide for students starting high school. The organization is responsible for a number of schools across the country, which train students on a more advanced level in each field of study.
		\end{rSubsection}
		
	\end{rSection}
	%----------------------------------------------------------------------------------------
	%	SKILLS SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{SKILLS}
		
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Programming Languages & C/C++, Python, R, MATLAB \\
			Web Technologies & HTML, CSS, Javascript, MySQL \\
			Libraries & numPy, Pandas \\
			Operating Systems & Linux, Windows\\
			Languages & Persian, English \\
			Miscellaneous & \LaTeX, Jupyter, Microsoft Office, GAMS, Database Design\\
		\end{tabular}
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%----------------------------------------------------------------------------------------
	%	REFERENCES SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{REFERENCES}
		\begin{itemize}{\bfseries}
			\item {\bfseries Andrea Bunt}\\
			Professor at the University of Manitoba\hfill	\href{bunt at cs.umanitoba.ca}{bunt at cs.umanitoba.ca}
			
			\item {\bfseries Mohammad Akbari}\\
			Assistant Professor at Amirkabir University of Technology \hfill	\href{akbari.ma@aut.ac.ir}{akbari.ma@aut.ac.ir}

			\item {\bfseries Fatemeh Zare-Mirakabad}\\
			Assistant Professor / Head of CS Group at Amirkabir University of Technology\hfill	\href{f.zare@aut.ac.ir}{f.zare@aut.ac.ir}
			

						
	\end{itemize}
	
	\end{rSection}
	
	%----------------------------------------------------------------------------------------

	
\end{document}
